\documentclass[11pt]{article}
\usepackage[scale=0.875, stdmathitalics=false, stdmathdigits=false]{lucimatx}
\linespread{1.02}

% alt to lucimatx
% \usepackage{times}
% \usepackage{amsmath}
% \usepackage{amssymb}

\usepackage{graphicx}

\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\pdfpagewidth=\paperwidth
\pdfpageheight=\paperheight

\setlength{\textwidth}{7.5in}
\setlength{\textheight}{10.1in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\topmargin}{-0.8in}
\setlength{\headsep}{0pt}

\def\arraystretch{1.15}
\raggedbottom
\sloppy

\newcommand{\proficient}[1]{{\slshape #1}}
\newcommand{\expert}[1]{{\slshape\bfseries #1}}
\newcommand{\heading}[1]{{\sc\bfseries #1}}
\newcommand{\spell}[1]{{\sc\bfseries\large #1}}
\newcommand{\available}{{\Large $\boxtimes$}\ }

\newcommand{\mycheckbox}{{\Large $\Box$}}
\newcommand{\checkboxTwo}{{\Large $\Box \, \Box$}}
\newcommand{\checkboxThree}{{\Large $\Box \, \Box \, \Box$}}
\newcommand{\checkboxFour}{{\Large $\Box \, \Box \, \Box \, \Box$}}
\newcommand{\checkboxFive}{{\Large $\Box \, \Box \, \Box \, \Box \, \Box$}}
\newcommand{\checkboxTen}{\checkboxFive \ \ \ \ \checkboxFive}

\begin{document}
\pagestyle{empty}
\noindent
{\huge\bfseries Iain McEwan, Occultist}
\hfill
{\Large Scotsman}
\hfill
{\Large Neutral-Good}
\hfill
{\Large Level 3}
\\[-8pt]
\hrule

\mbox{ }
\\[6pt]
\heading{Sex}: Male
\ \ \ \
\heading{Height}: 5'\,9''
\ \ \ \
\heading{Weight}: 11 stone
\ \ \ \
\heading{Hair}: Black
\ \ \ \
\heading{Eyes}: Blue

\noindent
\begin{tabular}[t]{|r|c|l|c|}
\hline
\heading{Ability}
& \heading{Score (Mod)}
& \heading{Save}
\\ \hline \hline
\sc Strength & 11 \ (+0)
& +3
\\
\sc Constitution & 9 \ (+0)
& +3
\\ \hline
\sc Dexterity & 13 \ (+1)
& +5
\\
\sc Speed & 17 \ (+2)
& +5
\\ \hline
\sc Marksmanship & 11 \ (+0)
& +3
\\
\sc Perception & 9 \ (+0)
& +3
\\
\sc Acuity & 17 \ (+2)
& +5
\\ \hline
\sc Reason & 17 \ (+2)
& +5
\\
\sc Will & 14 \ (+1)
& +4
\\
\sc Charisma & 14 \ (+1)
& +4
\\ \hline
\end{tabular}
\hfill
\begin{tabular}[t]{|r|c|}
\hline
\sc Defense & +7
\\
\sc Proof & +3
\\ \hline
\sc Initiative & +2
\\
\sc Act (Move) & 4 (3)
\\  \hline
\sc Cast Bonus & +4
\\ \hline
\sc Melee & +2
\\
\sc Firearm & +2
\\
\sc Missile & +0
\\ \hline
\sc Melee DC & d6
\\
\sc Firearm DC & d6
\\ \hline
\sc Heal Rate & +2
\\ \hline
\end{tabular}
%
\hfill
%
\begin{tabular}[t]{|r|c|c|}
\hline
\sc Experience & \multicolumn{2}{|l|}{27,195}
\\
(bank) & \multicolumn{2}{|l|}{2125}
\\ \hline
\sc Hit Points & 47 & \hspace*{10em}
\\
(wounded) & (-35) &
\\[6pt] \hline
\sc Qi &  45 &
\\ (scratch) & (-31) &
\\[2pt] \hline
\sc Arcanum & 11 &
\\[2pt] \hline
\sc Bandages & 10 &
\\[2pt] \hline
\sc Smite, Blade & 18 &
\\[2pt] \hline
\sc Karma & 29 &
\\ \hline
\end{tabular}
%
\\[8pt]
%
\noindent
\begin{tabular}[t]{|r|crl|c|l|}
\hline
\sc\bfseries Weapon
& \sc\bfseries Avail
& \sc\bfseries Damage
& \sc\bfseries Type
& \sc\bfseries Range
& \sc\bfseries Properties
\\ \hline\hline
Superior (+2) Saracen Blade & +5 & d6 + d8 & piercing & --- &
\\ \hline
Superior (+2) New Land Cavalary Pistol & +6 & 5d6 & piercing
& & ranged, Quality (+1) holster
\\
Quality (+1) French Pistol & +5 & 5d6 & piercing &  & ranged
\\
Quality (+1) AN IX Pistol & +5 & 5d6 & piercing &  & ranged
\\ \hline
\end{tabular}
%
\\[12pt]
%
\begin{tabular}[t]{|r|c|c|c|c|}
\hline
%
\heading{Martial Art} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Pistol & 2 & +4 & firearm & A
\\
\sc Sword & 1 & +3 & melee & A
\\[12pt] \hline \hline
%
\heading{Knowledge} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Metaphysics & 6 & +9 & rea, auth & C
\\
\sc Medicine & 1 & +3 & reason & C
\\
\sc Chemistry & 1 & +3 & reason & D
\\
\sc Fantastic Bestiary & 1 & +3 & reason & D
\\
\sc Nat Philosophy & 3 & +3 & reason & D
\\
\sc Symbols \& Rituals & 4 & +3 & reason & D
\\
\sc Orders \& Socs & 3 & +3 & reason & D
\\
\sc Signals \& Ciphers & 1 & +3 & reason & D
\\[12pt] \hline \hline
%
\heading{Skill} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Surgery & 5 & +7 & acuity & B
\\
\sc Mechanic & 2 & +5 & dexterity & C
\\
\sc Cunning Works & 2 & +3 & dexterity & B
\\
\sc Locksmithing & 1 & +3 & acuity & B
\\
\sc Seamanship & 2 & +4 & reason & C
\\
\sc Tracking & 1 & +3 & acuity & B
\\ \hline
\end{tabular}
%
\ \ \ \ \
%
\begin{tabular}[t]{|r|c|c|c|c|c|}
\hline
%
\heading{Talent} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Espionage & 4 & +6 & reason & B
\\
\sc Guile & 1 & +2 & charisma & B
\\
\sc Mimicry & 1 & +1 & perception & B
\\
\sc Ninjutsu & 1 & +3 & acuity & B
\\
\sc Riding & 1 & +2 & dexterity & D
\\
\sc Swimming & 1 & +1 & strength & D
\\
\sc Visual Arts & 2 & +3 & dexterity & D
%
\\[12pt] \hline \hline
%
\heading{Language} & \heading{Level} & \heading{Speak} & \heading{Write} & \heading{XP}
\\ \hline \hline
\sc English & 3 & yes & yes & D
\\
\sc Gaelic & 3 & yes & yes & D
\\
\sc French & 2 & yes & yes & D
\\
\sc Spanish & 2 & yes & yes & D
\\
\sc Latin & 2 & yes & yes & D
\\
\sc Greek & 1 & no & yes & D
\\
\sc Arabic & 1 & no & yes & D
\\
\sc Prot-Algonq & 1 & gesture & no & D
\\
\sc Orc & 1 & yes & no & D
\\
\sc Muskegee & 1 & yes & no & D
\\
\sc Flash & 1 & yes & no & D
\\ \hline
\end{tabular}

\clearpage
\noindent
{\sc\bfseries\Large Spells}
\vspace*{4pt}
\hrule
% \mbox{ }
% \\
% \noindent
% \begin{tabular}[t]{|r||c|c|}
% \hline
% \heading{Spell} & \heading{Cast Bonus}
% \\ \hline \hline
% \heading{Occultist} & +1 (+2 through buckle)
% \\ \hline
% \end{tabular}
%
\mbox{ }
\\[12pt]
%
\spell{Deflection Field} 1;
\ \textsc{Cost} 1 pt/phase;
\ \textsc{Casting time} 8 phases;
\ \textsc{Difficulty} 14;
\ \textsc{Range} self;
\ \textsc{Zone of Effect} Self;
\ \textsc{Duration} caster's discretion;
\ \textsc{Manifestation} instant;
\ \textsc{Type} vital forces / minor;
\\
\noindent\textsl{The Caster can create an energy field around his body
  that causes physical objects to deflect. Attackers suffer a
  $- (\mathrm{d4} + \mathrm{lvl})$ modifier when using melee weapons
  or projectiles. The field does not protect against energy based
  attacks or Magick. The field travels with the Caster.}
%
\\[6pt]
%
\spell{Deform} 1;
\ \textsc{Cost} resistance;
\ \textsc{Casting Time} resistance phases;
\ \textsc{Difficulty} resistance;
\ \textsc{Range} 9 squares;
\ \textsc{Zone of Effect} single object;
\ \textsc{Manifestation} Instant;
\ \textsc{Type} material world / minor;

\noindent\textsl{The Caster has the power to deform matter. He has
  limited control over how the material alters it's shape, but can
  specify: bend left/right, toward/away, along vertical/horizonal
  axis, diagonally. If the Cast is a success a d20 is rolled, the
  higher the roll the closer the new form is to the Caster's intent.}
%
\\[6pt]
%
\spell{Detect Magick} 1;
\ \textsc{Cost}	8;
\ \textsc{Casting Time}	12 phases;
\ \textsc{Difficulty} 12;
\ \textsc{Range} 9 squares;
\ \textsc{Manifestation} Instant;
\ \textsc{Duration of Effect} Single Event;

\noindent\textsl{The Caster can sense if an object or area produces an Occult
  emmination. The Caster has a limited ability to determine the
  strength of the aura. The presence of an aura does not mean the
  object posses magical powers, the object may have been constructed
  using magic or have been the subject of a spell. The Caster can
  detect magic on one object or one hex per Lvl. Some objects or
  locations may have been the subject of spells meant to conceal their
  magical nature in which case the GM may increase the Difficulty.}
%
\\[6pt]
%
\spell{Insinuate} 2;
\ \textsc{Cost} Subject's Will;
\ \textsc{Casting Time} 2 Turns
\ \textsc{Difficulty} Subject's Will;
\ \textsc{Range} Conversation;
\ \textsc{Zone of Effect} Individual;
\ \textsc{Manifestation} Instant;
\ \textsc{Duration of Effect} Single Event;
\ \textsc{Type} Mortal Sphere/Minor;

\noindent\textsl{The Caster can influence or "nudge" a Subject to
  perform a specified action. The Subject will perform the act and
  remember doing so without reflection until questioned about the
  action by another. The GM may modify the Difficulty of the spell
  based on the Subject's resistance to the action or feelings toward
  the Caster. This modifier is added to cost of casting.}
%
\\[6pt]
%
\spell{Magick Missile} 4;
\ \textsc{Range} 18 squares;
\ \textsc{Damage} 6d6;
\ \textsc{Type} Spiritual Realm/Minor;
\ \textsc{Difficulty} Will save modified by proficiency level;
\ \textsc{Zone of Effect} Individual;
\ \textsc{Cost} 1/2 pt. per pt. of damage;
\ \textsc{Casting Time} 7 Phases;
\ \textsc{Duration of Effect} Single Event;
\ \textsc{Manifestation} Instant;
\ \textsc{Range} [Will+ Lvl] Hexes;

\noindent\textsl{The Caster focuses a charge of Qi energy and projects
  it at a foe. To determine "To Hit" treat Will as Mrk and use Casting
  Bonus as a modifier. If the Caster hits 2d4 + 1d4 (?) per Lvl is
  inflicted. If the Caster misses two Qi points are expended.}
%
\\[6pt]
%
\spell{Recktify} 1;
\ \textsc{Range} 1 square;

\noindent\textsl{Remove one condition.}
%
\\[6pt]
%
\spell{Revive} 1
\ \textsc{Type} Mortal Sphere/Minor;
\ \textsc{Difficulty} 13;
\ \textsc{Zone of Effect} Individual;
\ \textsc{Cost} 10;
\ \textsc{Casting Time} 8 phases;
\ \textsc{Duration of Effect} n/a;
\ \textsc{Manifestation} Instant;
\ \textsc{Range} Touch

\noindent\textsl{The Caster can negate the effects of "Reeling",
  "Dazed", "Stunned", unconciousness, "Fatigued", and "Seriously
  Wounded".}
%
\\[6pt]
%
\spell{Sonic Wave Manipulation} 1;
\ \textsc{Range} 15 squares;
\ \textsc{Type} Vital Forces/Minor;
\ \textsc{Difficulty} 13;
\ \textsc{Zone of Effect} 1 Hex per Lvl;
\ \textsc{Cost} 5+1/2 pt per phase;
\ \textsc{Casting Time}	14;
\ \textsc{Duration of Effect} Caster's Discretion;
\ \textsc{Manifestation} Instant;
\ \textsc{Range} Will feet + 1 hex / lvl

\noindent\textsl{The Caster can alter the length of soundwaves as well as their
direction. The Caster can focus sound creating a parabolic mic to
eavesdrop or "throw" sounds to make them seem to come from another or
multiple directions. The Caster can also raise or lower the pitch of
sounds or distort sound waves to create various acoustic effects.}
%
\\[6pt]
%
\spell{Sonic Flux} 1;
\ \textsc{Zone} 1 square;
\ \textsc{Range} 2 squares;
\ \textsc{Type} Vital Forces/Minor;
\ \textsc{Difficulty} 14;
\ \textsc{Zone of Effect} 1 Hex per Lvl;
\ \textsc{Cost} See Discription;
\ \textsc{Casting Time} 15 phases;
\ \textsc{Duration of Effect} Caster's Discretion;
\ \textsc{Manifestation} Instant;
\ \textsc{Range} 1/2 Will ft;

\noindent\textsl{The Caster can reduce/increase all sound within 1 Hex per Spell Lvl by
one sound lvl per Spell Lvl.Cost: 1pt. per Hex affected+1pt. per sound
lvl altered+1pt per phase maintained.}

% \spell{Shockwave} 1;
% \ \textsc{Zone of Effect} 3 squares;
% \ \textsc{Range} 4 squares

\clearpage
\noindent
{\sc\bfseries\Large Baggage}
\vspace*{4pt}
\hrule
\mbox{ }
\\[4pt]
%
\heading{Weapons:}
\ Superior (+2) Saracen Blade (scimitar) d8;
\ Superior (+2) New Land Cavalry Pistol 4d6;
\ Quality (+1) French Pistol 4d6;
\ Quality (+1) AN IX Pistol 4d6;
\ +1 Holster;
%
\\[6pt]
%
\heading{Armor:}
\ \textsc{Elven Cloak with Mitrhil Plates and Elven Belt} +3 defense (quality cloak
+1, mithril plates +2), +1 concealment;
\ \textsc{Wolf Fang Totem} +1 defense, +1 save vs. magic (on leather thong);
\ \textsc{Living Beast Jumpsuit} +3 defense, +3 proof, grey metallic,
jumpsuit feels like fabric, chameleon powers
%
\\[6pt]
%
\heading{Baggage Extraordinaire:}
\ \textsc{Spyglass} by Leonoardo Semitecolo of Veneto (8" collapsed, 22" extended);
\ \textsc{Holster} Quality (+1) (conceal +1);
\ \textsc{Wolf Moccasins} Quality (+1) from Black Wolf's wife (dex
save +1; move silently +1);
\ \textsc{Jeweler's Loup} Quality (+1);
\ \textsc{Lizardman ``Axe'' Blades} d4 damage, from past age;
\ \textsc{Moonvision Snuff Box} (2) doses moonvision
%
\\[6pt]
%
\heading{Baggage Pecuniary:}
\ 4 gold sovereigns sewn into cloak;
\ money purse with silvers and coppers;
\ small strongbox from contact in DC;
%
\\[6pt]
%
\heading{Baggage Mundane:}
\ quick match/seal acid (24 pts);
\ decorative beads on drawstrings on cloak create 1' x 1' sealer when
blended to bum up locks, seal doors, etc;
\ portable writing desk with straps, papers, obfuscating sealing wax;
%
\\[6pt]
%
\heading{Surgery Kit:}
\ secret compartments;
\ poultices --- dried moss in bundles (2d4 heal potions each);
\ silken embroidery thread and silk shirt bandages;
\ medical sutures, surgical tubing, clamps
\ tongs, scalpels, bonesaw, lancets, needles;
\ laudanum and leather bit
%
\\[6pt]
%
\heading{Spell Focus:}
\ \textsc{Hibernian Buckle}
\ +1 saves;
\ +1 cast bonus;
\ from past age given by Stands-on-Dry-Land
%
\\[6pt]
%
\heading{Baggage Arcane:}
\ \textsc{Elven Talisman} soothes savage beast to avoid sleepwalking
as wolf;
\ \textsc{Pepper Box Elemental Pistol:} one orc wildcard charge left
%
\\[6pt]
%
\heading{Baggage Natural:}
\ \textsc{Man-Thing Swamp Beast Blood};
\ \textsc{Orc, Orco-Bugbear, Bugbear Ears} from Ottawa;
\ \textsc{Sabretooth Tiger tooth} from past;
\ \textsc{Dragodile Sack Juice} (3) 17-intensity bile;
\ \textsc{Kobold Fungus} (2) 14-intensity poison;
\ \textsc{Gymsum Weed} induces trance---from Ottawans;
\ \textsc{Wall Glue} held trepanned orc to wall in FL;
%
\\[6pt]
%
\heading{Baggage Grimoire:}
\
\textsc{Huerta's Bible} {\it gave to Kolancha}, leather-bound with
Spanish and arcane markings, cabalistic runes with Aztec, Latin,
Spanish, Incan, some copies with numbers/transposition, Ponce de Leon,
and a body of water;
\ \
\textsc{James Cox's Manual of Automata} {\it only skimmed};
\ \
\textsc{History of Crusades} {\it skimmed Library of congress to learn
  of crusades, templars, etc.};
\ \
\textsc{Dr.\ Manticore's Book of Voodo} symbolic loas, Haitian
spirits, and locksmithing (!);
\ \
\textsc{Polynesian Tattoos and Markings} from tradition of Jugdish's
Northstar tatoo;
\ \
\textsc{Habits of Natives of Florida} Jesuitical father authored;
\ \
\textsc{Survey Southern Florida Coasts and Waterways} 1760s, some
outdated/bandoned English settlements, author;
\ \
\textsc{A Physician's Guide to the Occult} Iain's own sketches and
notes on fantastic beasts, items, rituals, and locations
\\[6pt]
\heading{Aliases:} \ White Skinwalker; \ White Wolf; \ Isaac Hayes; \
Rodney Allen Rippey
%

\clearpage
\pagestyle{empty}
\noindent
{\huge\bfseries Lobo-Iain}
\hfill
{\Large Werewolf}
\hfill
{\Large Chaotic-Good}
\hfill
{\Large Level 3}
\\[-8pt]
\hrule

\mbox{ }
\\[6pt]
\heading{Sex}: Male
\ \ \ \
\heading{Height}: 6'\,3''
\ \ \ \
\heading{Weight}: 16 stone
\ \ \ \
\heading{Hair}: Black
\ \ \ \
\heading{Eyes}: Blue

\noindent
\begin{tabular}[t]{|r|c|l|c|}
\hline
\heading{Ability}
& \heading{Score (Mod)}
& \heading{Save}
\\ \hline \hline
\sc Strength & 15 \ (+1)
& +4
\\
\sc Constitution & 14 \ (+1)
& +4
\\ \hline
\sc Dexterity & 15 \ (+1)
& +4
\\
\sc Speed & 18 \ (+3)
& +6
\\ \hline
\sc Marksmanship & 11 \ (+0)
& +3
\\
\sc Perception & 9 \ (+0)
& +3
\\
\sc Acuity & 18 \ (+3)
& +6
\\ \hline
\sc Reason & 9 \ (+0)
& +3
\\
\sc Will & 14 \ (+1)
& +4
\\
\sc Charisma & 14 \ (+1)
& +4
\\ \hline
\end{tabular}
\hfill
\begin{tabular}[t]{|r|c|}
\hline
\sc Initiative & d10 + 3
\\
\sc ACT & 5 (2)
\\  \hline
\sc Melee & +5
\\
\sc Firearm & +0
\\
\sc Missile & +0
\\ \hline
\sc Melee DC & 1d8
\\ \hline
\sc Healing Rate & +2
\\ \hline
\sc Defense & +8
\\
\sc Proof & +3
\\ \hline
\end{tabular}
%
\hfill
%
\begin{tabular}[t]{|r|c|c|}
\hline
\sc Experience & \multicolumn{2}{|l|}{N/A}
\\
(bank) & \multicolumn{2}{|l|}{N/A}
\\ \hline
\sc Hit Points & 63 & \hspace*{8em}
\\
(wounded) & (-46) &
\\[2pt] \hline
\sc Karma & 28 &
\\ \hline
\end{tabular}
%
\\[8pt]
%
\noindent
\begin{tabular}[t]{|r|crl|c|l|}
\hline
\sc\bfseries Weapon
& \sc\bfseries Avail
& \sc\bfseries Damage
& \sc\bfseries Type
& \sc\bfseries Range
& \sc\bfseries Properties
\\ \hline\hline
Claws & +8 & d6 + d8 & slashing & ---
& d6 + d10 + 3 when wounded
\\
Fangs & +8 & 2d8 & piercing & ---
& Savage, d8 + d10 + 3 w.~w.
\\
Flying Attack & +7 & d8 + d10 + 1 / square & piercing & ---
& Savage Attack, d8 + d12 + 3 + 1 / square w.~w.
\\ \hline
\end{tabular}
%
\\[12pt]
%
%
\begin{tabular}[t]{|r|c|c|c|c|}
\hline
%
\heading{Martial Art} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Claws & 3 & +8 & melee & A
\\
\sc Fangs & 3 & +8 & melee & A
\\
\sc Flying Attack & 1 & +7 & melee & A
\\ \hline
\end{tabular}
%
\ \ \ \ \ \
%
\begin{tabular}[t]{|r|c|c|c|c|}
\hline
\heading{Skill} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Tracking & 1 & +4 & acu & n/a
\\ \hline \hline
%
\heading{Talent} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Guile & 1 & +2 & charisma & n/a
\\
\sc Ninjutsu & 1 & +4 & acuity & n/a
\\
\sc Swimming & 1 & +2 & strength & n/a
\\ \hline
\end{tabular}
%
\mbox{ }
\\[-12pt]
\heading{Transform}: 9 phases to transform
%
\\[4pt]
%
\heading{Night Vision}: 30'
%
\\[4pt]
%
\heading{Savage Attack}: After a bite, Strength (18) vs. Strength
roll for additional 1d8 damage.
%
\\[4pt]
%
\heading{Blood Curdling Howl}: Short action encounter power.
\\
The Beast's baleful cry freezes its victims with fear.  A CHR (15) vs
WILL CRR, (character level + 2) squares radius effect, is made and all
affected Subjects are paralyzed until the end of the Beast's next
Action.  If attacked by the Beast before the Effect ends, the Subject
suffers a DEF loss equal to the Beasts character level plus CHR ABM
(+4, total).
%
\\[4pt]
%
\heading{Fury of the Beast}: There's nothing more dangerous than a
wounded animal and the Beast is no exception.  Once Seriously
Wounded, 1) the Beast's Melee DC shifts up to 1d10, (2) it adds +3 damage,
3) it gains CON temp HPs [14], and 4) it never suffers the Seriously
Wounded modifier.

Once the Beast's Hit Points fall to zero or below, it reverts to its
human form and has zero Hits.  A Death Save is required before
healing.
%
\\[4pt]
%
\heading{Track of the Beast}: The Beast Ignores Difficult Terrain and
can enter and occupy half squares.  If knocked Prone, the Beast can
continue fighting without suffering any Combat Loss.
%
\\[4pt]
%
\heading{Natural Fur}: +2 defense from fur.  Adds 1 to Iain's defense.
%
\\[4pt]
%
\heading{Flying Attack}:  The attacker moves at least one square in an
unobstructed path to target and makes an attack.  If successful, make
Speed save modified by attribute bonus and proficiency level in Flying
Attack.

If fails, attack goes through as normal.  If successful, the Attacker
shifts Melee Damage class up one and add +1 damage per square traversed.

Flex may not be allocated to Defense.  May be combined with Iaijutsu.
\end{document}