\documentclass[11pt]{article}
\usepackage[scale=0.875, stdmathitalics=false, stdmathdigits=false]{lucimatx}
\linespread{1.02}

% alt to lucimatx
% \usepackage{times}
% \usepackage{amsmath}
% \usepackage{amssymb}

\usepackage{graphicx}

\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\pdfpagewidth=\paperwidth
\pdfpageheight=\paperheight

\setlength{\textwidth}{7.5in}
\setlength{\textheight}{10.1in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\topmargin}{-0.8in}
\setlength{\headsep}{0pt}

\def\arraystretch{1.15}
\raggedbottom
\sloppy

\newcommand{\proficient}[1]{{\slshape #1}}
\newcommand{\expert}[1]{{\slshape\bfseries #1}}
\newcommand{\heading}[1]{{\sc\bfseries #1}}
\newcommand{\spell}[1]{{\sc\bfseries\large #1}}
\newcommand{\available}{{\Large $\boxtimes$}\ }

\newcommand{\mycheckbox}{{\Large $\Box$}}
\newcommand{\checkboxTwo}{{\Large $\Box \, \Box$}}
\newcommand{\checkboxThree}{{\Large $\Box \, \Box \, \Box$}}
\newcommand{\checkboxFour}{{\Large $\Box \, \Box \, \Box \, \Box$}}
\newcommand{\checkboxFive}{{\Large $\Box \, \Box \, \Box \, \Box \, \Box$}}
\newcommand{\checkboxTen}{\checkboxFive \ \ \ \ \checkboxFive}

\begin{document}
\pagestyle{empty}
\noindent
{\huge\bfseries Jugdish, Devotee of Ganesh}
\hfill
{\Large East Indian}
\hfill
{\Large Neutral-Good}
\hfill
{\Large Level 3}
\\[-8pt]
\hrule

\mbox{ }
\\[6pt]
\heading{Sex}: Male
\ \ \ \
\heading{Height}: 5'\,7''
\ \ \ \
\heading{Weight}: 13 stone
\ \ \ \
\heading{Hair}: Black
\ \ \ \
\heading{Eyes}: Hazel

\noindent
\begin{tabular}[t]{|r|c|l|c|}
\hline
\heading{Ability}
& \heading{Score (Mod)}
& \heading{Save}
\\ \hline \hline
\sc Strength & 15 \ (+1)
& +4
\\
\sc Constitution & 16 \ (+2)
& +6
\\ \hline
\sc Dexterity & 18 \ (+3)
& +6
\\
\sc Speed & 14 \ (+1)
& +4
\\ \hline
\sc Marksmanship & 9 \ (+0)
& +3
\\
\sc Perception & 9 \ (+0)
& +4
\\
\sc Acuity & 12 \ (+1)
& +4
\\ \hline
\sc Reason & 11 \ (+0)
& +4
\\
\sc Will & 18 \ (+3)
& +9
\\
\sc Charisma & 14 \ (+1)
& +4
\\ \hline
\end{tabular}
\hfill
\begin{tabular}[t]{|r|c|}
\hline
\sc Defense & +7
\\
\sc Proof & +3
\\ \hline
\sc Initiative & +1
\\
\sc Act (Move) & 5 (2)
\\  \hline
\sc Cast Bonus & +4
\\ \hline
\sc Melee & +5
\\
\sc Firearm & +0
\\
\sc Missile & +3
\\ \hline
\sc Melee DC & d8
\\
\sc Firearms DC & d6
\\ \hline
\sc Healing Rate & +1
\\ \hline
\end{tabular}
%
\hfill
%
\begin{tabular}[t]{|r|c|c|}
\hline
\sc Experience & \multicolumn{2}{|l|}{27,510}
\\
(bank) & \multicolumn{2}{|l|}{10}
\\ \hline
\sc Hit Points & 56 & \hspace*{8em}
\\
(wounded) & (-42) &
\\[2pt] \hline
\sc Qi &  58 &
\\ (scratch) & (-39) &
\\[2pt] \hline
\sc Arcanum & 5 &
\\[2pt] \hline
\sc Ritual Heal & d4 + 3 &
\\[2pt] \hline
\sc Smite, Club & 16 &
\\[2pt] \hline
\sc Karma & 26 &
\\ \hline
\end{tabular}
%
\\[8pt]
%
\noindent
\begin{tabular}[t]{|r|crl|c|l|}
\hline
\sc\bfseries Weapon & \sc\bfseries Avail & \sc\bfseries Damage
& \sc\bfseries Type & \sc\bfseries Range & \sc\bfseries Properties
\\ \hline\hline
Quality (+1) Shawnee Club & +11 & d6 + d8 & bludgeoning & ---
& +4 smite damage
\\ \hline
Typical (+0) Fowling Musket & +1 & 5d6 & piercing & & ranged
\\ \hline
\end{tabular}
%
\\[12pt]
%
\begin{tabular}[t]{|r|c|c|c|c|}
\hline
%
\heading{Knowledge} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Etiquette & 2 & +2 & rea & D
\\
\sc Theology & 5 & +5 & rea & C
\\
\sc Symbols \& Rituals & 1 & +1 & rea & D
\\[12pt] \hline \hline
%
\heading{Skill} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Forgery & 1 & +4 & dex & C
\\
\sc Farming / Livestock & 1 & +2 & acuity & D
\\
\sc Gunnery & 1 & +2 & acuity & D
\\
\sc Observation & 1 & +2 & acuity & D
\\
\sc Seamanship & 3 & +6 & dex & C
\\[12pt] \hline \hline
%
\heading{Talent} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Acrobatics & 4 & +7 & dex & B
\\
\sc Climbing & 2 & +5 & dex & B
\\
\sc Concealment & 1 & +1 & per & B
\\
\sc Escape & 1 & +4 & dex & B
\\
\sc Ninjutsu & 1 & +4 & dex & B
\\
\sc Riding & 1 & +4 & dex & D
\\
\sc Scrounging & 1 & +1 & per & C
\\
\sc Swimming & 2 & +4 & con & D
\\ \hline
\end{tabular}
%
\ \ \ \ \
%
\begin{tabular}[t]{|r|c|c|c|c|c|}
\hline
%
%
\heading{Martial Art} & \heading{Level} & \heading{Tot} & \heading{Basis} & \heading{XP}
\\ \hline \hline
\sc Clubs \& Maces & 4 & +10 & melee, ritual +1 & A
\\
\sc Shoulder Arm & 1 & +1 & firearm & A
\\
\sc Iaijutsu & 1 & +6 & melee & A
\\[12pt] \hline \hline
%
\heading{Language} & \heading{Level} & \heading{Speak} & \heading{Write} & \heading{XP}
\\ \hline \hline
\sc Hindi & native & yes & yes & D
\\
\sc Sanskrit & fluent & yes & yes & D
\\
\sc English & fluent & yes & yes & D
\\
\sc French & conv. & yes & no & D
\\
\sc Spanish & conv. & yes & no & D
\\
\sc Arabic & basic & yes & yes & D
\\
\sc Prot-Algonq & basic & gesture & no & D
\\ \hline
\end{tabular}

\clearpage
\noindent
{\sc\bfseries\Large Spells}
\vspace*{4pt}
\hrule
%
\mbox{ }
\\[12pt]
%
\spell{Awe} 3;
\ \textsc{Cast Time} 10 phases;
\ \textsc{Cost} 5 + 1 per target + targets' will bonuses;
\ \textsc{Zone of Effect} 1 target / level;
\ \textsc{Range} will/2 + level;
\ \textsc{Difficulty} victim's will;
\ \textsc{Duration} 2--5 actions + level
\\
\textsl{The caster manifests the Terror and Majesty of his or her god inducing
a state of Awe in the beholder.  If succesful, the Caster rolls 1d6
with the following effect per victim.  1--4: stand agog, \, 5: abase;
\, 6: flee.  While the effect lasts, the victim cannot perform any
other Action.  Attacking the victim breaks the spell.}
%
\\[4pt]
%
\spell{Dispel Magic} 1;
\ \textsc{Cast Time} 8 phases;
\ \textsc{Difficulty} will vs. will CRR modified by proficiency level;
\ \textsc{Cost} will + level;
\ \textsc{Range} will + level;
\\
\textsl{The caster can stop the manifestation of another Caster's
  spell.  Dispell does not undo the effects of a spell, it simply ends
  it.  The CRR BCS is modified by both Caster's Prof. Level.}
%
\\[4pt]
%
\spell{Eyes of Ganesh} 2;
\ \textsc{Cost} 6 qi / hour;
\\
\textsl{See in dark.  At 3rd level, see magical darkness, illusions, etc.}
%
\\[4pt]
%
\spell{Grace} 1;
\\
\textsl{Improves Knowledge, Talent, or Skill Roll.}
%
\\[4pt]
%
\spell{Heal} 2;
\ \textsc{Casting Time} 8 phases;
\ \textsc{Range} touch;
\ \textsc{Cost} 1/2 per HP;
\\
\textsl{Battlefield max d8 per level.}
%
\\[4pt]
%
\spell{Karmic Blessing}
%
\\
\textsl{Devotee feat;  add karma to any roll.}
%
\\[4pt]
\spell{Levitate} 3; \ \textsc{Difficulty} 12; \ \textsc{Range} 5
squares;
\\
\textsl{The Caster can move himself or an object up to will + 5'/level
  in any diection.  The path of movement is a straight line and is
  stopped by any barrier.  Upon reaching the maximum distance, the
  Caster can hover with an additionl Qi expenditure.  Cost ---
  small object: 2 (hover 1/2 per action), self: 5 + 1/2 pt / foot
  (hover 1 per action), large: 10 + 1 pt / foot (hover 2 per action),
  very large: 20 + 2 pt / foot (hover 4 per action).}
%
\\[4pt]
%
\spell{Reach of Ganesh} 1;
\ \textsc{Range} 2 squares;
\ \textsc{Damage} 1d8;
\ \textsc{Cast roll} 11;
\\
\textsl{At end of attack, make second attack roll.}
%
\\[4pt]
%
\spell{Smite} 3;
\ \textsc{Range} touch;
\ \textsc{Resolution} uncontested;
\ \textsc{Duration} sustained;
\ \textsc{Difficulty} critical miss fizzles;
\ \textsc{Cost} divine power invested / 2;
\ \textsc{Cast Time} 2 extended actions;
\ \textsc{Type} lesser pious devotion
\\
\textsl{The Devotee can invest a weapon with divine power, increasing
the damage inflicted in battle.  Each time the wielder wounds an
Opponent a Damage Avail equal to the Caster's Charisma Modifier plus proficiency
level is added and the value of the smite deducted from Divine Power
Amount.
\\[2pt]
The amount of power a weapon can contain: inferior 10 pts, standard 14
pts; quality 16 pts; superior 18 pts; matchless 20 pts; arcane
25 pts;
\\[2pt]
A weapon invested with Smite is treated as an Arcane Weapon when used
against creatures immune to Mundane attackes.
\\[2pt]
If the devotee fails his cast roll, there is a 50\% chance the weapon
will be destroyed.}
%
\\[4pt]
%
\spell{Summon Beast} 1;
\ \textsc{Cast Time} 15 phases;
\ \textsc{Difficulty} 13;
\ \textsc{Cost} 5 + circumstances (distance, state of animal, prior
contact);
\ \textsc{Range} 350' / level;
\\
\textsl{Call animal at random or specific to caster; beast only
  compelled to approach.}

\clearpage
\noindent
{\sc\bfseries\Large Baggage}
\vspace*{4pt}
\hrule
\mbox{ }
\\[4pt]
\heading{Weapons:}
\ Superior (+2) Dwarven Handaxe d8;
\ Quality (+1) Shawnee Club d6;
\ Quality (+1) Scimitar of Toledo Steel d8;
\ Fowling Musket 5d6;
%
\\[6pt]
%
\heading{Armor:}
\ \textsc{Elven Cloak with Mitrhil Plates} +3 defense (quality cloak
+1, mithril plates +2), +1 concealment;
\ \textsc{Mammoth's Coat} +1 defense, +6 proof vs.\ cold, neverending rope
\ \textsc{Living Beast Jumpsuit} +3 defense, +3 proof, grey metallic,
jumpsuit feels like fabric, chameleon powers
%
\\[6pt]
%
\heading{Baggage Extraordinaire:}
\ \textsc{Moonvision Snuff Box} (2) doses moonvision;
\ \textsc{Dwarven Beard Stiffener} (3) doses, 8 hps continuing to temp
HPs
\ \textsc{Wraith} (3), whoosh, black smoke, purple flash, 15' radius,
wraith comes out wails, and flies up;
\ \textsc{Orcseeker} tear off end, pour into muzzle, drop rocket,
illuminate 50' areas for 12 phases, orcish blood fluoresces;
\ \textsc{Incendiary Cable} (3') 1' burns through 1.5" of steel;
\ \textsc{Vitrifying Agent}: red flask and blue flask, swab on end,
red first, then blue, 1' x 1' cube vitrifies;
%
\\[6pt]
%
\heading{Baggage Pecuniary:}
4 gold sovereigns sewn into cloak;
\ concealed money purse with 50 Spanish silver coins
%
\\[6pt]
%
\heading{Baggage Mundane:}
\ climbing kit with 100' rope, hammer, pitons;
\ candles, tinder, flints, bullseye lantern;
\ sewing kit;
\ soap and towel;
\ keys to DC safe house (Dahlia housekeeper)
%
\\[6pt]
%
\heading{Baggage Arcane:}
\ \textsc{Northstar Tattoo:} +1 boon constancy/immovability Will and Con,
and +1 boon navigation Perception and Knowledge,
from Australian sailor on ship from Polynesian tattoo book;
\ \textsc{Mastodon Tusk Talisman:} spell focus;
\ \textsc{Silver Bosun's Whistle:} calls Sugarfoot; 2 notes to call
back, Sugarfoot swims
%
\\[6pt]
\heading{Aliases:} \ Antonio Fargas; \ Gary Coleman; \ Chaka Khan
%
\end{document}