\documentclass[11pt]{article}
\usepackage[scale=0.875, stdmathitalics=false, stdmathdigits=false]{lucimatx}
\linespread{1.02}

% alt to lucimatx
% \usepackage{times}
% \usepackage{amsmath}
% \usepackage{amssymb}

\usepackage{graphicx}

\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\pdfpagewidth=\paperwidth
\pdfpageheight=\paperheight

\setlength{\textwidth}{7.5in}
\setlength{\textheight}{10.1in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\topmargin}{-0.75in}
\setlength{\headsep}{0pt}

\def\arraystretch{1.15}
\raggedbottom
\sloppy

\newcommand{\proficient}[1]{{\slshape #1}}
\newcommand{\expert}[1]{{\slshape\bfseries #1}}
\newcommand{\heading}[1]{{\sc\bfseries #1}}
\newcommand{\spell}[1]{{\sc\bfseries #1}}
\newcommand{\available}{{\Large $\boxtimes$}\ }

\newcommand{\mycheckbox}{{\Large $\Box$}}
\newcommand{\checkboxTwo}{{\Large $\Box \, \Box$}}
\newcommand{\checkboxThree}{{\Large $\Box \, \Box \, \Box$}}
\newcommand{\checkboxFour}{{\Large $\Box \, \Box \, \Box \, \Box$}}
\newcommand{\checkboxFive}{{\Large $\Box \, \Box \, \Box \, \Box \, \Box$}}
\newcommand{\checkboxTen}{\checkboxFive \ \ \ \ \checkboxFive}

\begin{document}
\pagestyle{empty}
\noindent
{\huge\bfseries The Grim Kharthaxis}
\hfill
{\Large Bronze Dragonborn}
\hfill
{\Large Paladin 8;  Ranger 3}

\hrule

\mbox{ }
\\[6pt]
\heading{Sex}: Male
\ \ \ \
\heading{Height}: 6'4''
\ \ \ \
\heading{Weight}: 250 lbs.
\ \ \ \
\heading{Hair}: ---
\ \ \ \
\heading{Eyes}: Gold
\\[4pt]
\heading{Alignment}: Lawful Good
\ \ \ \
\heading{Deity}: The Storm
\ \ \ \
\heading{Faction}: Order of the Gauntlet
\\[12pt]
%
\begin{tabular}{|r|c|l|r|}
\hline
\heading{Ability}
& \heading{Score (Mod)}
& \heading{Skills}
& \heading{Save}
\\ \hline \hline
\sc Strength & 20 \ (+5)
& \proficient{Athletics +9}
& +9
\\
\sc Dexterity & 10 \ (+0)
& Acrobatics +0 \ \ Sleight of Hand +0 \ \ Stealth +0
& +4
\\
\sc Constitution & 16 \ (+3)
&
& +7$^\dagger$
\\ \hline
\sc Intelligence & \hspace*{0.2em} 8 \ (\hspace*{0.25em}-1)
& Arcana -1 \ \ History -1$^\dagger$ \ \ Investigation -1 \ \ Nature -1 \ \ \proficient{Religion +3}
& +3
\\
\sc Wisdom & 10 \ (+0)
& Animals +0 \ \ \proficient{Insight} +4 \ \ Medicine +0 \ \ Perception +0 \ \ \proficient{Survival +4}\hspace{0.75pt}$^\dagger$
& \proficient{+8}
\\
\sc Charisma & 18 \ (+4)
& Deception +4 \ \ \proficient{Intimidation +8} \ \ Performance +4 \ \ \proficient{Persuasion + 8}$\hspace{1pt}^\dagger$
& \proficient{+12}
\\ \hline
\end{tabular}
\\[2pt]
$^\dagger$\hspace*{-1pt}{\small\heading{Advantages}:
\ {\it Con Save}: concentration;
\ {\it History, Persuasion}: dwarves;
\ {\it Survival}: favored terrain \& enemies;
\ {\it Initiative}
\\
\heading{Resistances}: lightning
\ \ \ \ \
\heading{Immunities}: disease

\noindent
\begin{tabular}[t]{|r|c|}
\hline
\sc\bfseries AC & 20
\\
\sc\bfseries \mbox{ } \ \ +1 shield & 23
\\ \hline
\sc\bfseries Initiative & +0$^\dagger$
\\ \hline
\sc\bfseries Speed & 30'
\\ \hline \hline
\sc\bfseries Proficiency & +4
\\ \hline
\end{tabular}
%
\hspace*{12pt}
%
\begin{tabular}[t]{|r|crl|c|l|}
\hline
\sc\bfseries Weapon
& \sc\bfseries Attack
& \sc\bfseries Damage
& \sc\bfseries Type
& \sc\bfseries Range
& \sc\bfseries Properties
\\ \hline\hline
+2 Greathammer & +11 & 2d6 + 7 & bludgeoning & --- & heavy, 2H
\\
+2 Javelin(s) & +11 & 1d6 + 7 & piercing & 45 / 180 & ranged, thrown
\\ \hline
Breath Weapon & DC 15 dex & 4d6 & lightning & 5' x 30' line & ranged
\\
Unarmed & +9 & 1d1 + 5 & bludgeoning & --- & ---
\\ \hline
\end{tabular}

\mbox{ } \vspace*{12pt} \mbox{ }

\noindent
\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
\hline
\heading{Hit} \hspace*{6em}
                 & \heading{Temp} & \heading{Hit}  & \heading{Death} & \heading{Lay on} \hspace*{3em}
                                                                                       & \heading{Breath} &                 & \heading{Channel}  & \heading{Divine}
\\[-4pt]
\heading{Points} & \heading{HP}   & \heading{Dice} & \heading{Save}  & \heading{Hands} & \heading{Weapon} & \heading{Lucky} & \heading{Divinity} & \heading{Sense}
\\ \hline
{\bf 103} / long & & {\bf 11} / long & & {\bf 40} / long & {\bf 1} / short & {\bf 3} / long & {\bf 1} / short & {\bf 4} / long
\\ \hline \hline
& & & \hfill {\small \sc Succ:} \checkboxThree & &  & & &
\\
& & & \hfill {\small\sc Fail:} \checkboxThree & & & & &
\\ \hline
\end{tabular}

\mbox{ }\\[4pt]
%
\heading{Armor}: heavy, shields
\ \ \ \
\heading{Weapons}: martial, simple
\ \ \ \
\heading{Languages}:  Common, Draconic, Dwarvish, Abyssal
\\[8pt]
%
\heading{Natural Explorer}:
\ 1) advantage on initiative;
\ 2) advantage on first turn vs.\ creatures who haven't acted;
\ 3) ignore difficult terrain;
\ 4) stealth at normal pace
\\[4pt]
\heading{Extra Attack}: Attack twice when using attack action.
\\[4pt]
\heading{Horde Breaker}: Once per turn, make another attack vs. different creature in range and within 5' of target.
\\[4pt]
\heading{Divine Smite}: After hit, spell slot to deal +2d8 melee damage; +1d8 per level above 1st; +1d8 vs.\ undead.
\\[4pt]
\heading{Lucky}: replace your or opponent's d20 rolls for attack, ability check, or saving throw after seeing result.
\\[4pt]
\heading{Vow of Enmity} (channel divinity): As bonus action, utter vow vs.\ creature in 10' for attack advantage for 1 minute.
\\[4pt]
\heading{Relentless Avenger}: After opportunity hit, move half speed w/o provoking opportunitie attacks.
\\[4pt]
\heading{Warcaster}:
\ 1) advantage con save to concentrate;
\ 2) somatic while armed;
\ 3) spell as opportunity attack.
\\[4pt]
\heading{Favored Enemy}: {\it Undeads and Fiends}.
\ 1) +2 damage;
\ 2) advantage on Wisdom (Survival) checks to track
\\[4pt]
\heading{Abjure Enemy} (channel divinity): As action, one creature in 60' makes Wisdom save (fiends undead have disadvantage) or frightened speed zero, else speed halved.
\\[8pt]
%
\heading{Aura of Protection}: +4 saving throws for you and friendly creatures within 10' (included).
\\[4pt]
\heading{Lay on Hands}: As action, touch creature to restore HPs or spend 5 to cure one disease or poison.
\\[4pt]
\heading{Healer}:
\ 1) healer's kit yields 1 hp;
\ 2) healer kit gives 1d6 + 4 as action (once max per short rest)
\\[4pt]
\heading{Divine Health}: Immune to disease.
\\[4pt]
\heading{Resistance to Ligntning}: Half damage from lightning.
\\[8pt]
%
\heading{Darkvision}: 60' range dim light perceived as bright, darkness as dim.
\\[4pt]
\heading{Divine Sense}: As action, locate celestial, fiend or undead or consecration in 60' not behind total cover.
\\[4pt]
\heading{Primeval Awareness}: Use spell slot to focus awareness to sense whether one type of creature is within one mile of you (five in favored terrain).
\\[4pt]
\heading{Favored Terrain}: {\it Mountains and Hills}.
\\[4pt]
\heading{Natural Explorer (cont.)}:
\ 5) remain alert while traveling;
\ 6) friends ignore difficult terrain traveling;
\ 7) successful Wisdom (Survival) track reveals number, size, and time frame of creatures tracked
\\[8pt]
%
\heading{Shelter the Faithful}: Free lodging and care at temples of your faith.
\\[4pt]
\heading{Defense Style}: +1 defense while wearing armor (included).
\\[4pt]
\heading{Two Weapon Style}: Add ability modifier to second weapon attack (included).
\\[4pt]

\noindent
{\sc\bfseries\Large Possessions}
\vspace*{4pt}
\hrule
\mbox{ } \\[4pt]
\noindent
\heading{Orphan Fund}: 7020;  \ \ \ \ \heading{Collection Plate}: 3125
\\[4pt]
\heading{+2 Mithril/Black Dragon Fin Javelins}: matched pair with sympathetic magic;  dwarven throwers that return to hands on command as interact with object;  +50\% range (included).  Attuned.
\\[4pt]
\heading{+2 Greathammer}: Durgeddin forged, dwarven artifact.  Attuned.
\\[4pt]
\heading{+1 Plate Armor}
\\[8pt]
\heading{Boots of Elvenkind}: Advantage on stealth to be quiet
\\[4pt]
\heading{Belt of Dwarvenkind}: +2 constitution to max 20; advantage on Charisma (Perception) with dwarves; advantage on save vs. pison; resistance to poison; speak, read, write Dwarvish.  Attuned.
\\[4pt]
\heading{Immovable Rod}
\\[8pt]
\heading{Healing Potion {\bf (4)}}: (action to consume for 2d4 + 4 HPs)
\\[4pt]
\heading{Dwarven Draught {\bf (1)}}: action to consume for 20 HPs, cure one condition (2nd dose causes drunken exhaustion)
\\[8pt]
\heading{Healing Kit} {\bf (4)}: stabilize at 1hp as action;  d6 + 1 hps as action (per rest)
\\[8pt]
\heading{Baggage Arcane}: Bag of Holding; +1 Dwarven Battleaxe (Hew); +1 Red Dragon Scale Shield; +1 Elven Longbow;  +1 Dwarven Warhammer; striped toadstool (poisonous); Jeralla's Dragon Head Chest
\\[4pt]
\heading{Baggage Mundane}: signet ring order of Gauntlet; signet ring from Trasander House;  Cult of the Dragon robes and amulet; suit of fine clothing; holy symbol; prayer book; 100' elven rope; mundane dwarven helm;  Myth Drannor emerald necklace; mapper's compass; splint mail; explorer's pack
\\[12pt]


\noindent
{\LARGE Background}
\hrule

\mbox{ }
\\[8pt]
%
\heading{Lineage}: The Grim Kharthaxis comes from a long line of paladins, their function is to protect the temples and guard the priests when they travel.
\\[4pt]
%
\heading{Background}: Acolyte
\\[4pt]
\heading{Ideal}:  Thunder knows not pity, nor lightning mercy.
\\[4pt]
%
\heading{Flaw}:  The law is the law and he does not question it.
\\[4pt]
%
\heading{Paladin Oath of Vengeance}:
\ 1) fight greater evil;
\ 2) no mercy for wicked;
\ 3) achieve goals by any means necessary;
\ 4) restitution must be made.
\\[4pt]
%
\heading{Ranger Archetype Hunter}: included above

\clearpage
\noindent
{\sc\bfseries\Large Spellcasting}
\vspace*{4pt}
\hrule
\mbox{ }
\\
\noindent
\begin{tabular}[t]{|r||c|c|}
\hline
\heading{Spell} & \heading{Save DC} & \heading {Attack Modifier}
\\ \hline \hline
\heading{Paladin} & 16 & +8
\\ \hline
\heading{Ranger} & 12 & +4
\\ \hline
\end{tabular}
%
\ \ \ \
%
\begin{tabular}[t]{|r|l|}
\hline
\heading{Level} & \heading{Spell Slots} / long rest
\\ \hline \hline
{\sc 1st} & \checkboxFour
\\
{\sc 2nd} & \checkboxThree
\\
{\sc 3rd} & \checkboxThree
\\ \hline
\end{tabular}

\mbox{ }
\\[-6pt]
\heading{Paladin Spells Prepared}:  8 / long rest

\mbox{ }
\\
{\Large Paladin Spells, 1st Level}
\hrule

\mbox{ }
\\[6pt]
\available \spell{Bane} (Oath): 1 action; 30'; V,S,M; 1 minute
\\
{\small Up to three creatures of your choice that you can see within
  range must make Charisma saving throws. Whenever a target that fails
  this saving throw makes an attack roll or a saving throw before the
  spell ends, the target must roll a d4 and subtract the number rolled
  from the attack roll or saving throw.}
\\
{\footnotesize\slshape When you cast this spell using a spell slot of
  2nd level or higher, you can target one additional creature for each
  slot level above 1st.}
\\[4pt]
\available \spell{Hunter's Mark} (Oath): 1 bonus action; 90'; V; 1
hour
\\
You choose a creature you can see within range and mystically mark it
as your quarry. Until the spell ends, you deal an extra 1d6 damage to
the target whenever you hit it with a weapon attack, and you have
advantage on any Wisdom (Perception) or Wisdom (Survival) check you
make to find it. If the target drops to 0 hit points before this spell
ends, you can use a bonus action on a subsequent turn of yours to mark
a new creature.

At Higher Levels. When you cast this spell using a spell slot of 3rd
or 4th level, you can maintain your concentration on the spell for up
to 8 hours. When you use a spell slot of 5th level or higher, you can
maintain your concentration on the spell for up to 24 hours.
\\[4pt]
$\Box$ \spell{Bless}: 1 action; 30'; V,S,M; concentration 1 minute
\\
You bless up to three creatures of your choice within range. Whenever
a target makes an attack roll or a saving throw before the spell ends,
the target can roll a d4 and add the number rolled to the attack roll
or saving throw.

At Higher Levels. When you cast this spell using a spell slot of 2nd
level or higher, you can target one additional creature for each slot
level above 1st.
\\[4pt]
$\Box$ \spell{Command}: 1 action; 60'; V; 1 round
\\
You speak a one-word command to a creature you can see within
range. The target must succeed on a Wisdom saving throw or follow the
command on its next turn. The spell has no effect if the target is
undead, if it doesn’t understand your language, or if your command is
directly harmful to it.  Some typical commands and their effects
follow. You might issue a command other than one described here. If
you do so, the GM determines how the target behaves. If the target
can’t follow your command, the spell ends.

{\small
{\it Approach}. The target moves toward you by the shortest
  and most direct route, ending its turn if it moves within 5' of
  you.

{\it Drop}. The target drops whatever it is holding and then ends
  its turn.

{\it Flee}. The target spends its turn moving away from you by the
  fastest available means.

{\it Grovel}. The target falls prone and then ends its turn.

{\it Halt}. The target doesn’t move and takes no actions. A flying
  creature stays aloft, provided that it is able to do so.
}

\noindent
At Higher Levels. When you cast this spell using a spell slot of 2nd
level or higher, you can affect one additional creature for each slot
level above 1st. The creatures must be within 30 feet of each other
when you target them.
\\[4pt]
$\Box$ \spell{Compelled Duel}: 1 bonus action; 30'; V; conc. 1 minute
\\
One creature that you can see must make a Wisdom save. On a failed
save, the target has disadvantage on attack rolls against creatures
other than you, and must make a Wisdom save each time it tries to move
to a space that's more than 30 feet away from you. If it passes, its
movement isn't restricted for that turn.

The spell ends if you attack any other creature, if you cast a spell that targets a hostile creature other than the target, if a creature friendly to you damages the target or casts a harmful spell on it, or if you end your turn more than 30 feet away from the target.
\\[4pt]
$\Box$ \spell{Cure Wounds}: 1 action; touch; V,S; instantaneous
\\
A creature you touch regains a number of hit points equal to 1d8 +
Charisma modifier.  This spell has no effect on undead or constructs.

At Higher Levels: When you cast this spell using a spell slot of 2nd
level or higher, the Healing increases by 1d8 for each slot level
above 1st.
\\[4pt]
$\Box$ \spell{Detect Evil and Good}: 1 action or 10m ritual; self (30'); V,S; concentration 10 minutes
\\
For duration, know if aberration, celestial, elemental, fey, fiend, or undead within 30' as well as where located.  Also know consecrated or descrated places in range. Can penetrate most materials other than 1' stone, 1'' metal, thin lead, 3' wood or dirt.
\\[4pt]
$\Box$ \spell{Detect Magic}: 1 action or 10m ritual; self; V,S; concentration 10 minutes
\\
For duration, sense presence of magic within 30'.  Use your action to detect aura and school of magic.  Can penetrate most materials other than 1' stone, 1'' metal, thin lead, 3' wood or dirt.
\\[4pt]
$\Box$ \spell{Detect Poison and Disease}: 1 action or 10m ritual; self (30'); V,S,M (yew leaf); 10 minutes with concentration
\\
Sense presence of poisons, poisonous creatures, and diseases and identify it.  Spell blocked by 1 foot stone, 1 inch metal, thin sheet lead, 3 feet wood or dirt.
\\[4pt]
$\Box$ \spell{Divine Favor}: 1 bonus action; self; V,S; 1 minute
\\
Your prayer empowers you with divine radiance. Until the spell ends, your weapon attacks deal an extra 1d4 radiant damage on a hit.
\\[4pt]
$\Box$ \spell{Heroism}: 1 action; touch; V,S; 1 minute
\\
A willing creature you touch is imbued with bravery. Until the spell
ends, the creature is immune to being frightened and gains temporary
hit points equal to your spellcasting ability modifier at the start of
each of its turns. When the spell ends, the target loses any remaining
temporary hit points from this spell.

At Higher Levels. When you cast this spell using a spell slot of 2nd
level or higher, you can target one additional creature for each slot
level above 1st.
\\[4pt]
$\Box$ \spell{Protection from Evil and Good}: 1 bonus action; touch; V,S,M; 10 minutes with concentration
\\
One willing creature protected against aberrations, celestials, elementals, fey, fiends, and undead.  Creatures of those types have disadvantage on attacks vs. target. Target can't be charmed, frightened or possessed by them.  If already charmed, frightened, or possessed, target has advantage on saves.
\\[4pt]
$\Box$ \spell{Purify Food and Drink}: 1 action or 10m ritual; 10'; V,S; instantaneous
\\
All nonmagical food and drink within 5' radius sphere is rendered free of poison and disease.
\\[4pt]
$\Box$ \spell{Searing Smite}: 1 bonus action; self; V; conc. up to 1
minute
\\
The next time you hit a creature with a melee weapon attack, the
attack deals an extra 1d6 fire damage to the target and sets them on
fire. The fire goes out if the spell is ended.

At the start of each of its turns, the target must make a Constitution
saving throw. On a failure, it takes 1d6 fire damage. On a success,
the spell ends. If the target or a creature within 5 feet of it uses
an action to put out the flames, or if some other effect douses the
flames, the spell ends.

At Higher Levels: The initial extra damage dealt by the attack
increases by 1d6 for each slot above 1st.
\\[4pt]
$\Box$ \spell{Shield of Faith}: 1 bonus action; 60'; V,S,M; 10 minutes
with concentration
\\
Shimmering field surrounds creature of choice granting it +2 AC for
the duration.
\\[4pt]
$\Box$ \spell{Thunderous Smite}: 1 bonus action; self; V; conc. up to
1 minute
\\
The first time you hit with a melee weapon attack, your weapon makes a
thunderous boom that spans 300 feet from you. The attack deals an
extra 2d6 thunder damage. Additionally, if the target is a creature,
it must succeed on a Strength save or be pushed 10 feet away from you
and knocked prone.
\\[4pt]
$\Box$ \spell{Wrathful Smite}: 1 bonus action; self; V; conc. up to 1
minute
\\
The next time you hit with a melee weapon attack, it deals an extra 1d6 psychic damage. Additionally, if the target is a creature, it must pass a Wisdom save or be frightened of you until the spell ends. As an action, the creature can make a Wisdom save against your spell save DC to end this spell.
\\[12pt]


\noindent
{\Large Paladin Spells, 2nd Level}
\hrule

\mbox{ }
\\[6pt]
\available \spell{Hold Person} (oath): 1 action; 60'; V,S,M; 1 minute
\\
Choose a humanoid that you can see within range. The target must succeed on a Wisdom saving throw or be paralyzed for the duration. At the end of each of its turns, the target can make another Wisdom saving throw. On a success, the spell ends on the target.

At Higher Levels. When you cast this spell using a spell slot of 3rd
level or higher, you can target one additional humanoid for each slot
level above 2nd. The humanoids must be within 30 feet of each other
when you target them.
\\[4pt]
\available \spell{Misty Step} (oath): 1 bonus action; self; V; instant
\\
Briefly surrounded by silvery mist, you teleport up to 30 feet to an
unoccupied space that you can see.
\\[4pt]
$\Box$ \spell{Aid}: 1 action; 30'; V,S,M; 8 hours
\\
Your spell bolsters your allies with toughness and resolve. Choose up
to three creatures within range. Each target’s hit point maximum and
current hit points increase by 5 for the duration.

At Higher Levels. When you cast this spell using a spell slot of 3rd
level or higher, a target’s hit points increase by an additional 5 for
each slot level above 2nd.
\\[4pt]
$\Box$ \spell{Branding Smite}: 1 bonus action; self; V; conc. up to 1
minute
\\
The next time you hit a creature with a weapon attack before this
spell ends, the weapon gleams with astral radiance as you strike. The
attack deals an extra 2d6 radiant damage to the target, which becomes
visible if it's invisible, and the target sheds dim light in a 5-foot
radius and can't become invisible until the spell ends.

At Higher Levels. When you cast this spell using a spell slot of 3rd
level or higher, the extra damage increases by 1d6 for each slot level
above 2nd.
\\[4pt]
$\Box$ \spell{Find Steed}: 10 minutes; 30'; V,S; instant
\\
You summon a spirit that assumes the form of an unusually intelligent,
strong, and loyal steed, creating a long-lasting bond with
it. Appearing in an unoccupied space within range, the steed takes on
a form that you choose: a warhorse, a pony, a camel, an elk, or a
mastiff. (Your GM might allow other animals to be summoned as steeds.)
The steed has the statistics of the chosen form, though it is a
celestial, fey, or fiend (your choice) instead of its normal
type. Additionally, if your steed has an Intelligence of 5 or less,
its Intelligence becomes 6, and it gains the ability to understand one
language of your choice that you speak.

Your steed serves you as a mount, both in combat and out, and you have
an instinctive bond with it that allows you to fight as a seamless
unit. While mounted on your steed, you can make any spell you cast
that targets only you also target your steed.

When the steed drops to 0 hit points, it disappears, leaving behind no
physical form. You can also dismiss your steed at any time as an
action, causing it to disappear. In either case, casting this spell
again summons the same steed, restored to its hit point maximum.

While your steed is within 1 mile of you, you can communicate with it
telepathically.  You can’t have more than one steed bonded by this
spell at a time. As an action, you can release the steed from its bond
at any time, causing it to disappear.
\\[4pt]
$\Box$ \spell{Lesser Restoration}: 1 action; touch; V,S; instant
\\
You touch a creature and can end either one disease or one condition
afflicting it. The condition can be blinded, deafened, paralyzed, or
poisoned.
\\[4pt]
$\Box$ \spell{Locate Object}: 1 action; self; V,S,M; 10 minutes
\\
Describe or name an object that is familiar to you. You sense the
direction to the object’s location, as long as that object is within
1,000 feet of you. If the object is in motion, you know the direction
of its movement.

The spell can locate a specific object known to you, as long as you
have seen it up close—within 30 feet—at least once. Alternatively, the
spell can locate the nearest object of a particular kind, such as a
certain kind of apparel, jewelry, furniture, tool, or weapon.  This
spell can’t locate an object if any thickness of lead, even a thin
sheet, blocks a direct path between you and the object.
\\[4pt]
$\Box$ \spell{Magic Weapon}:  1 bonus action; touch; V,S; 1 hour
\\
You touch a nonmagical weapon. Until the spell ends, that weapon becomes a magic weapon with a +1 bonus to attack rolls and damage rolls.

At Higher Levels. When you cast this spell using a spell slot of 4th
level or higher, the bonus increases to +2. When you use a spell slot
of 6th level or higher, the bonus increases to +3.
\\[4pt]
$\Box$ \spell{Protection from Poison}: 1 action; touch; V,S; 1 hour
\\
You touch a creature. If it is poisoned, you neutralize the poison. If
more than one poison afflicts the target, you neutralize one poison
that you know is present, or you neutralize one at random.

For the duration, the target has advantage on saving throws against
being poisoned, and it has resistance to poison damage.
\\[4pt]
$\Box$ \spell{Zone of Truth}: 1 action; 60'; V,S; 10 minutes
\\
You create a magical zone that guards against deception in a
15-foot-radius sphere centered on a point of your choice within
range. Until the spell ends, a creature that enters the spell’s area
for the first time on a turn or starts its turn there must make a
Charisma saving throw. On a failed save, a creature can’t speak a
deliberate lie while in the radius. You know whether each creature
succeeds or fails on its saving throw.

An affected creature is aware of the spell and can thus avoid
answering questions to which it would normally respond with a
lie. Such a creature can be evasive in its answers as long as it
remains within the boundaries of the truth.
\\[12pt]

\noindent
{\Large Ranger Spells, 1st Level}
\hrule

\mbox{ }
\\[6pt]
\available \spell{Hail of Thorns}: 1 bonus action; self; V; conc. up
to 1 minute
\\
The next time you hit with a ranged weapon attack, in addition to the
normal effects of the attack, the target and each creature within 5
feet of it must make a Dexterity save. A creature takes 1d10 piercing
damage on a failed save, or half as much on a success.
\\[4pt]
\available \spell{Ensnaring Strike}: 1 bonus action; self; V; conc. up
to 1 minute
\\
The next time you hit a creature with a weapon attack, the target must
succeed on a Strength save or be restrained until the spell ends. A
Large or bigger creature has advantage on this save.

While restrained by this spell, the target takes 1d6 piercing damage
at the start of each of its turns. The creature restrained or one that
can touch the creature can use its action to make a Strength check
against your spell save DC. On a success, the target is freed.

At Higher Levels: The damage increases by 1d6 for each slot level
above 1st.
\\[4pt]
\available \spell{Longstrider}: 1 action; touch; V,S,M; 1 hour
\\
You touch a creature. The target’s speed increases by 10 feet until
the spell ends.

At Higher Levels. When you cast this spell using a spell slot of 2nd
level or higher, you can target one additional creature for each slot
level above 1st.
\\[4pt]



\end{document}